MSCA 31006: Final Project - AQI Forecasting

### 2023-08-11 MSCA_31006_Time_Series_Final_Project.Rmd
Update MSCA_31006_Time_Series_Final_Project.Rmd

---
title: 'MSCA 31006: Final Project - AQI Forecasting'
author: "Aashish Singh"
date: "8/10/2023"
output: html_document
---

@@

shapiro.test(fresno_pm2_5_weekly_ts)

@@

>>>>

---
title: 'MSCA 31006: Final Project - AQI Forecasting'
author: "Aashish Singh, Jacob Brewer, Nikitha Gopal, Sydney Peters"
date: "8/10/2023"
output: html_document
---

@@

@@

#### Step 5: Look at ACF / PACF plots

```{r, tidy=TRUE}
acf(fresno_pm2_5_weekly_ts, main = "ACF of  Time Series")
pacf(fresno_pm2_5_weekly_ts, main = "PACF of Time Series")

plot(decompose(fresno_pm2_5_weekly_ts_transformed,type="additive"))

#### Step 5: Understand the composition of the time series data
```{r, tidy=TRUE}

#differencing data
# this can help stablise mean of time series by removing chnges in the level of a time series

fresno_pm2_5_weekly_ts_diff<- diff(fresno_pm2_5_weekly_ts)
plot(fresno_pm2_5_weekly_ts_diff)

acf(fresno_pm2_5_weekly_ts_diff, main = "ACF of differenced Time Series")
pacf(fresno_pm2_5_weekly_ts_diff, main = "PACF of differenced Time Series")

decomp <- decompose(fresno_pm2_5_weekly_ts, type="additive")
plot(decomp)
